The Forecast Trap

### 2022-04-09 manuscript/round4-manuscript.Rmd
here we go

I shall focus on examples involving fisheries management to illustrate principles shared in many ecological systems.
Fisheries are a significant economic and conservation concern worldwide and their management remains an important debate [e.g. @Worm2006; @Worm2009; @Costello2016].
Moreover, their management has been a proving grounds for theoretical and practical decision-making issues which are widely applicable in other areas of ecology and conservation [@Ludwig1993; @Lande1994], and one that has long wrestled with issues of uncertainty in the context of management decisions [e.g. @Clark1973; @Reed1979; @Walters1981; @Ludwig1982].

@@

The author acknowledges support from NSF CAREER Award #1942280 and helpful discussions with Melissa Chapman. The author is also deeply grateful to the Michael Runge and three other anonymous reviewers whose detailed feedback and insights have greatly shaped the paper and my own understanding of these issues.

>>>>

I shall focus on examples involving fisheries management to illustrate principles shared in many ecological systems.
Fisheries are a significant economic and conservation concern worldwide and their management remains an important debate [e.g. @Worm2006; @Worm2009; @Costello2016].
Moreover, their management has been a proving grounds for theoretical and practical decision-making issues [e.g. @Clark1973; @Reed1979; @Walters1981; @Ludwig1982] arising in a wide range of other contexts, including
invasive species [@Boettiger2021], infectious diseases [@Li2017; Shea2014], fire management [@Richards1999] conservation planning and priortization [@Chades2008; @Wilson2006] climate policy [@] and much else [@Ludwig1993; @Lande1994; @Polasky2011].

@@

The author acknowledges support from NSF CAREER Award #1942280 and helpful discussions with Melissa Chapman. The author is also deeply grateful to the Michael Runge, Chih-hao Hsieh, Antoine Brias, and other anonymous reviewers whose detailed feedback and insights have greatly shaped the paper and my own understanding of these issues.
